The intention of this research is twofold. Firstly overcoming the issue of deploying a single adaptive model to similar but slightly different navigation environments which learns from varying environments under varying conditions without affecting its existing knowledge and experience obtained from other environments. Having a single fixed deeper model is inefficient and even though the model after learned from diverse dataset will be able to generalize to all contexts might not producing best results in each context where a smaller model trained from that particular context only might perform better. Secondly training such system from real world diverse data as well as training in real time. 

We highlighted that the above mentioned needs are not yet fully addressed in the literature where existing researches either try to make pre-recorded dataset larger, or make the neural network deeper. Existing approaches to training does not fully solve the problem of training a navigation system in real world. We believe that training an agent in a simulated environment is not the solution since there is a considerable gap between real world and a simulated environment.

The research objectives include building a pure vision based end-to-end architecture for autonomous navigation which is based on conditionally generated contextualized feature maps which are dynamically adaptive to the environment and taking a promising approach to train such system in real world large scale diverse data. The models we develop are required to learn from slightly different environments while maintaining the experience learned from previous environments. Our research is inspired by the biological behavior of these particular tasks. 

To achieve these objectives a comprehensive research methodology was proposed which starts from a critical review of literature and gradually building required tools towards an end-to-end architecture which extracts both spatial and temporal information from the input in order to output navigation commands. Finally these individual tools will be assembled together in order to build the final system. Specific attention will be given to train the system from real world data taking a hybrid approach of existing learning methods. 